# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r ,echo=TRUE}
repdata<-read.csv("./activity/activity.csv", header=TRUE)
str(repdata)
```


## What is mean total number of steps taken per day?
```{r ,echo=TRUE}
dailysteps<-tapply(repdata$steps,repdata$date,sum,na.rm=TRUE)
hist(dailysteps,breaks=62,xlab="Total Daily Steps",main = paste("Histogram of Total Daily Steps"),)
```
The mean of daily total number of steps is
```{r ,echo=TRUE}
mean(dailysteps)
```

The median of daily total number of steps is
```{r ,echo=TRUE}
median(dailysteps)
```

## What is the average daily activity pattern?



## Imputing missing values
The total number of missing values in the dataset is :
```{r ,echo=TRUE}
length(which(is.na(repdata$steps)))
```

The filling strategy consists in replacing NAs values by daily mean of steps.
Here below the new dataset filled with this strategy :
```{r ,echo=TRUE}
newrepdata<-repdata
newrepdata$avg<-ave(repdata$steps,repdata$date,na.rm=TRUE)
newrepdata$steps[!is.na(newrepdata$steps)]<-newrepdata$avg[!is.na(newrepdata$steps)]
```
Here the new histogramm :
```{r ,echo=TRUE}
dailysteps<-tapply(newrepdata$steps,newrepdata$date,sum,na.rm=TRUE)
hist(dailysteps,breaks=62,xlab="Total Daily Steps",main = paste("Histogram of Total Daily Steps"),)
```
The new mean of daily total number of steps is
```{r ,echo=TRUE}
mean(dailysteps)
```

The new median of daily total number of steps is
```{r ,echo=TRUE}
median(dailysteps)

## Are there differences in activity patterns between weekdays and weekends?
